A generalized definition of multidimensional item response theory parameters

### 2022-07-19 output/paper_draft/paper_M2PLM_parameters.Rmd
Includes empirical example table in paper draft

```{r read-chunks}
read_chunk("src/Graphical_example_paper.R")
```

@@

@@

>>>>

@@

```{r read-chunks-graphical-example}
read_chunk("src/Graphical_example_paper.R")
```

@@

```{r reset-root-wd}
# Necessary for knitr to find the source file:
opts_knit$set(root.dir = ROOT_DIR)
```

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example.R")
```

```{r read-items, message=FALSE}
```

```{r orthogonal-params}
```

```{r oblique-params}
```

```{r params-table}
```

```{r compose-empirical-items-table}
```

```{r set-flextable-wd, cache=FALSE}
```

<!---BLOCK_LANDSCAPE_START--->

```{r empirical-items-table-out, cache=FALSE, tab.id="empirical-items-table-out", tab.cap="Item parameters for the empirical example"}
item_params_output
```

<!---BLOCK_LANDSCAPE_STOP--->
